flowCore: data structures package for flow cytometry data

### 2008-07-15 inst/doc/HowTo-flowCore.Rnw
upadates to the documentation
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@32724 bc3139a8-67e5-0310-9ffc-ced21a209358

<<SummarFilter, echo=true, results=verbatim>>=
summary(filter(fs[[1]], kmeansFilter("myKMeans","FSC-H"=c("Low", "Medium", "High"))))
@

@@

<<Norm2Filter, echo=true, results=verbatim>>=
morphGate <- norm2Filter(filterId="MorphologyGate", "FSC-H", "SSC-H", scale=2)
smaller <- Subset(fs, morphGate)
fs[[1]]
smaller[[1]]
@

@@

<<Split, echo=true, results=verbatim>>=
split(smaller[[1]], kmeansFilter("myKMeans","FSC-H"=c("Low","Medium","High")))
@

@@

<<Split2, echo=true, results=verbatim>>=
split(smaller, kmeansFilter("myKMeans", "FSC-H"=c("Low", "Medium", "High")))
@

@@

<<FilterSet1, echo=true, results=verbatim>>=
fset1 = filterSet(
	rectangleGate(filterId="Fluorescence Region","FL1-H"=c(50,100),
                      "FL2-H"=c(50,100)),
	norm2Filter(filterId="Morphology Gate","FSC-H","SSC-H",scale=2),
	~ `Fluorescence Region` & `Morphology Gate`,
	~ `Fluorescence Region` | `Morphology Gate`,
	Debris ~ ! `Morphology Gate`,
	~ `Fluorescence Region` %&% `Morphology Gate`
)
fset1

>>>>

<<SummarFilter, echo=true, results=verbatim>>=
summary(filter(fs[[1]], kmeansFilter("FSC-H"=c("Low", "Medium", "High"),
                                     filterId="myKMeans")))
@

@@

<<Norm2Filter, echo=true, results=verbatim>>=
morphGate <- norm2Filter("FSC-H", "SSC-H", filterId="MorphologyGate", 
                         scale=2)
smaller <- Subset(fs, morphGate)
fs[[1]]
smaller[[1]]
@

@@

<<Split, echo=true, results=verbatim>>=
split(smaller[[1]], kmeansFilter("FSC-H"=c("Low","Medium","High"),
                                 filterId="myKMeans"))
@

@@

<<Split2, echo=true, results=verbatim>>=
split(smaller, kmeansFilter("FSC-H"=c("Low", "Medium", "High"),
                            filterId="myKMeans"))
@

@@

<<FilterSet1, echo=true, results=verbatim>>=
fset1 = filterSet(
	rectangleGate(filterId="Fluorescence Region","FL1-H"=c(50,100),
                      "FL2-H"=c(50,100)),
	norm2Filter("FSC-H","SSC-H",filterId="Morphology Gate", scale=2),
	~ `Fluorescence Region` & `Morphology Gate`,
	~ `Fluorescence Region` | `Morphology Gate`,
	Debris ~ ! `Morphology Gate`,
	~ `Fluorescence Region` %&% `Morphology Gate`
)
fset1
